---
title: "linear model from Web"
author: "Anthony Benitez"
date: "Fall 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
basicNN <- ggplot(data,aes(y=ARM,x=SIMS))
basicNN + geom_point() + geom_lm()
```

This scatter plot shows us that we have a positive linear relationship, the fit line is going up to the right so that's how we could tell.






### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```

The correlation of SIMS and ARM is 0.68 so that number also tells us that we have a positive linear correlation.


### Inferential  (Build model.1)
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
#### Predict at target point
```{r}
mydat <- data.frame(GRIP = 94, ARM = 88)
```



```{r}
predict(model.1,mydat,interval = "prediction")
```

The target prediction is 0.70 the lower is -1.72 the upper is 3.13.

#### scatterplot with model fit
```{r}
basicNN <- ggplot(data,aes(y=ARM,x=SIMS))
basicNN + geom_point() + geom_lm()
``` 

## Model 2 SIM~GRIP

### Now add in scatterplot
```{r}
basicNG <- ggplot(data,aes(y=GRIP,x=SIMS))
basicNG + geom_point() + geom_lm()
```

We have a Positive line fit for SIMS and GRIP.

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```

The number that we got for the linear correlation is 0.63 that means we still have a positive linear correlation.

### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  



#### predict model.2 at target point
```{r}
mydat <- data.frame(GRIP = 94, ARM = 88)
```
```{r}
predict(model.2,mydat,interval = "prediction")
```

The prediction that we got was the fit is -0.536, the lower is -3.107, the upper is 2.035.

#### now add the model fit to our plot for model.2
```{r}
basicNG <- ggplot(data,aes(y=GRIP,x=SIMS))
basicNG + geom_point() + geom_lm()
```  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)
```{r}
cor(SIMS~ARM+GRIP,data=data)
```

The correlation number is 0.73 so we have a positive linear correlation.
  
### Inferential  (Build 2-dimentional model.3)
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
``` 
#### predict model.3 at target point
```{r}
predict(model.3,mydat,interval = "prediction")
```  

The linear fit is 0.149, the lower is -2.132, the upper is 2.431.

## Comparing nested models ANOVA Test



### Model.1 vs Model.3
```{r}
anova(model.1,model.3)
```

The anova test shows that model 3 is better than model 1.

### Model.2 vs Model.3
```{r}
anova(model.2,model.3)
```

The anova test shows that model 3 is better than model 2.

## Informally compare Model.1 with model.2
```{r}
anova(model.1,model.2)
```

The Model 1 was better than Model 2 because model 1's adjusted r square value was lower but from comparing them we didn't get a p value because neither model has any nested data in their models, but over all the best model that was better than 1 and 2 was model 3 it had the highest adjusted r squared and the lowest residual error number and we got a p value for model 3 because both model 1 and model 2 are nested in model 3.